---
title: "Hand-on Ex02"
format: html
execute:
  echo: false
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggrepel)
library(ggthemes)
library(patchwork)
exam <- read_csv("../data/Exam_data.csv")
```

## Improved Annotation with ggrepel
```{r}
p1 <- ggplot(exam, aes(x = MATHS, y = ENGLISH)) +
  geom_point() +
  geom_text(aes(label = ID), size = 2.5) +
  labs(title = "Standard Text Labels",
       x = "Maths Score", y = "English Score") +
  theme_minimal()

p2 <- ggplot(exam, aes(x = MATHS, y = ENGLISH)) +
  geom_point() +
  geom_text_repel(aes(label = ID), size = 2.5, max.overlaps = 15) +
  labs(title = "ggrepel Text Labels",
       x = "Maths Score", y = "English Score") +
  theme_minimal()

p1 + p2
```
The comparison demonstrates how ggrepel's text placement algorithm prevents overlapping labels, significantly improving readability compared to standard text annotations where labels obscure data points and each other.

## Professional Themes with ggthemes
```{r}
ggplot(exam, aes(x = MATHS, fill = GENDER)) +
  geom_histogram(bins = 20, position = "identity", alpha = 0.5) +
  labs(title = "Maths Score Distribution by Gender", 
       x = "Score", y = "Count") +
  theme_economist() +
  scale_fill_economist()
```
Using The Economist theme transforms the histogram into publication-quality visualization with distinctive typography and color palette, demonstrating how themed approaches can lend credibility and professionalism to statistical graphics.

## Typography-Focused Design
```{r}
ggplot(exam, aes(x = MATHS)) +
  geom_histogram(binwidth = 5, fill = "#A7C6DA", colour = "white") +
  labs(title = "Maths Score Distribution", 
       subtitle = "Enhanced typography for readability",
       x = "Score", y = "Count") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 14),
    text = element_text(family = "sans")
  )
```
The enhanced typography is achieved using ggplot2's native theming system with carefully adjusted text properties, creating a clean design with proper visual hierarchy and improved readability for reports and presentations.

## Composite Figures with Patchwork
```{r}
p1 <- ggplot(exam, aes(x = MATHS)) +
  geom_histogram(bins = 20, fill = "lightblue") +
  labs(title = "Maths Scores") +
  theme_minimal()

p2 <- ggplot(exam, aes(x = ENGLISH)) +
  geom_histogram(bins = 20, fill = "lightgreen") +
  labs(title = "English Scores") +
  theme_minimal()

p1 + p2
```
The side-by-side histograms created with patchwork enable efficient comparison of distributions between mathematics and English scores, revealing differences in central tendency and spread without requiring multiple separate figures.

## Multi-Row Layout
```{r}
p3 <- ggplot(exam, aes(x = MATHS, y = ENGLISH)) +
  geom_point() +
  labs(title = "Score Correlation") +
  theme_minimal()

(p1 + p2) / p3
```
This composite visualization integrates individual subject distributions with their correlation, creating a comprehensive analytical view that would otherwise require multiple separate charts, demonstrating patchwork's ability to build complex multi-level layouts.

## Auto-Tagged Composite Figure
```{r}
((p1 + p2) / p3) + plot_annotation(tag_levels = 'A')
```
Automatic tagging adds professional reference points to each panel, making the composite figure suitable for formal reports where specific panels need to be referenced in accompanying text.

## Inset Chart
```{r}
p3 + inset_element(p2, left = 0.6, bottom = 0.6, right = 1, top = 1)
```
The inset technique efficiently uses space by embedding the English score distribution within the correlation plot, allowing readers to reference the relevant distribution without switching between figures.

## Themed Composite Figure
```{r}
p1_themed <- p1 + theme_economist()
p2_themed <- p2 + theme_economist()
p3_themed <- p3 + theme_economist()

(p1_themed + p2_themed) / p3_themed
```
Combining patchwork with ggthemes creates professionally styled composite figures with consistent design elements across all panels, demonstrating how multiple extension packages can work together to produce polished statistical graphics.